Illuminating a Dark Lens : A Type Ia Supernova Magnified by \\ the Frontier Fields Galaxy Cluster Abell 2744

### 2015-08-11 APJ.submitted/snTomas.tex
Added a paragraph on flexion

\change{ One would expect that models incorporating weak-lensing
constraints would be less susceptible to such bias from a sharply
steepening mass profile.  However, we find that collectively the four
strong+weak lensing models (shown as diamonds in
Figure~\ref{fig:LensingTest}) exhibit the same propensity to
overestimate the magnification along this line of sight.  Thus, an
error in extrapolating the mass profile outside the strong lensing
region is not a likely explanation for the observed small systematic
bias.}

@@

@@

We have evaluated here only a single object behind a single cluster,
with a minor tension between the observed magnification and the model
predictions.  This is not in and of itself a cause for alarm.
Previous analyses of lensed \SNIa\ found no significant discrepancy
between the observed \SNIa\ magnifications and the predictions from
lens models (\citetalias{Patel:2014}; \citealt{Nordin:2014}), albeit
with a much smaller set of lens models being tested.  The observed
systematic bias for \tomas\ is small, and many of the lens models that
deviate from the measured magnification are preliminary models that
have not been updated to include all of the HFF data.  Future
revisions of the lens models for Abell 2744 could either incorporate
the observed magnification of \tomas\ as a new model constraint, or
can revisit this test to evaluate whether the bias persists.

@@

>>>>

\change{ One might expect that models incorporating weak-lensing
constraints would be less susceptible to such bias from a sharply
steepening mass profile.  However, we find that collectively the four
strong+weak lensing models (shown as diamonds in
Figure~\ref{fig:LensingTest}) exhibit the same propensity to
overestimate the magnification along this line of sight.  This
comparison therefore provides no evidence to support the extrapolation
error hypothesis. }

@@

\change{Given the intermediate location of this SN, caught between the
strong-lensing and weak-lensing regimes, an even more useful tool than
weak lensing would be the {\it flexion}
signal \citep{Goldberg:2002,Goldberg:2005,Irwin:2006,Goldberg:2007}.
Flexion is a second-order lensing effect that distorts the shapes of
background galaxies that are not lensed strongly enough to be warped
into arcs or filaments.  A flexion measurement near the SN \tomas\
sight line would be more sensitive to local gradients and substructure
in the cluster mass profile.  However, no such flexion constraints are
yet available.}

@@

We have evaluated here only a single object behind a single cluster,
with a minor tension between the observed magnification and the model
predictions.  This is not in and of itself a cause for alarm.
Previous analyses of lensed \SNIa\ found no significant discrepancy
between the observed \SNIa\ magnifications and the predictions from
lens models (\P14; \citealt{Nordin:2014}), albeit
with a much smaller set of lens models being tested.  The observed
systematic bias for \tomas\ is small, and many of the lens models that
deviate from the measured magnification are preliminary models that
have not been updated to include all of the HFF data.  Future
revisions of the lens models for Abell 2744 could either incorporate
the observed magnification of \tomas\ as a new model constraint, or
can revisit this test to evaluate whether the bias persists.

@@

\subsection{Future Work}
